---
title: "Combining_H07_June20"
author: "Hainan Xu"
date: "20/06/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE,warning=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The files 42 image samples of "H07-0500_79205589_179_MBP" and 42 ROI(return of information) tables. Here we convert the local coordinate to a global coordinate.
```{R message=FALSE, warning=FALSE}
library(dplyr)
library(readr)
library(tidyverse)

#first row
df1<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._01_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")

#x axis + 500
df2<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._02_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+500)
#x axis + 1000
df3<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._03_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+1000)

#second row
df4<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._04_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x,com_y=com_y+300)
#x axis + 500
df5<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._05_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+500,com_y=com_y+300)
#x axis + 1000
df6<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._06_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+1000,com_y=com_y+300)

#third row
df7<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._07_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x,com_y=com_y+600)
#x axis + 500
df8<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._08_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+500,com_y=com_y+600)
#x axis + 1000
df9<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._09_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+1000,com_y=com_y+600)

#fourth row
df10<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._10_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x,com_y=com_y+900)
#x axis + 500
df11<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._11_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+500,com_y=com_y+900)
#x axis + 1000
df12<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._12_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+1000,com_y=com_y+900)


#fifth row
df13<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._13_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x,com_y=com_y+300*4)
#x axis + 500
df14<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._14_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+500,com_y=com_y+300*4)
#x axis + 1000
df15<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._15_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+1000,com_y=com_y+300*4)

aa<-df15
aa[3]<-NULL

sum(duplicated(aa))

which(duplicated(aa))

aa[68,]

#sixth row
df16<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._16_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x,com_y=com_y+300*5)
dim(df1)
#x axis + 500
df17<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._17_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+500,com_y=com_y+300*5)
#x axis + 1000
df18<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._18_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+1000,com_y=com_y+300*5)

#seventh row
df19<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._19_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x,com_y=com_y+300*6)
dim(df1)
#x axis + 500
df20<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._20_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+500,com_y=com_y+300*6)
#x axis + 1000
df21<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._21_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+1000,com_y=com_y+300*6)

#eighth row
df22<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._22_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x,com_y=com_y+300*7)
#x axis + 500
df23<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._23_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+500,com_y=com_y+300*7)
#x axis + 1000
df24<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._24_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+1000,com_y=com_y+300*7)

#nineth row
df25<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._25_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x,com_y=com_y+300*8)
#x axis + 500
df26<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._26_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+500,com_y=com_y+300*8)
#x axis + 1000
df27<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._27_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+1000,com_y=com_y+300*8)

#tenth row
df28<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._28_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x,com_y=com_y+300*9)
#x axis + 500
df29<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._29_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+500,com_y=com_y+300*9)
#x axis + 1000
df30<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._30_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+1000,com_y=com_y+300*9)

#row 11
df31<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._31_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x,com_y=com_y+300*10)
#x axis + 500
df32<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._32_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+500,com_y=com_y+300*10)
#x axis + 1000
df33<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._33_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+1000,com_y=com_y+300*10)

#row 12
df34<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._34_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x,com_y=com_y+300*11)
#x axis + 500
df35<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._35_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+500,com_y=com_y+300*11)
#x axis + 1000
df36<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._36_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+1000,com_y=com_y+300*11)

#row 13
df37<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._37_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x,com_y=com_y+300*12)
#x axis + 500
df38<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._38_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+500,com_y=com_y+300*12)
#x axis + 1000
df39<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._39_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+1000,com_y=com_y+300*12)

#row 14
df40<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._40_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x,com_y=com_y+300*13)
#x axis + 500
df41<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._41_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+500,com_y=com_y+300*13)
#x axis + 1000
df42<-read_csv("/Users/hainanxu/Documents/spatial_visual_cortex/data/H07-0500_79205589_179_MBP/H07-0500_79205589_179_MBP._42_analysis_results.csv")%>%select("com_x","com_y","pixel_area","roi_source")%>%mutate(com_x=com_x+1000,com_y=com_y+300*13)

```
(com_x,com_y) is the center of the rectangular marker.
We combine the 42 dataframes and convert them into ppp object. After that,we compute the first order intensity as well as the nearest neighbor distance distribution. The distribution is right skewed. Also, it is noticable that there are 22 events whose nearest distance is smaller or euqal to 1.
```{R message=FALSE}
# there are 3604 points in total, 3604/36 \approx 100
df_full=rbind(df1,df2,df3,
              df4,df5,df6,
              df7,df8,df9,
              df10,df11,df12,
              df13   ,df14,df15,
              df16,df17,df18,
              df19,df20,df21,
               df22   ,df23,df24,
               df25   ,df26,df27     ,
              df28 ,df29,df30         ,
              df31,df32,df33,
              df34,df35,df36,
              df37,df38,df39,
              df40,df41,df42
              )

dim(df_full)

library("spatstat")
ln = with(df_full,
  ppp(x = com_x, y = com_y, marks = pixel_area, xrange = range(com_x), yrange = range(com_y)))
d = density(subset(ln), edge=TRUE, diggle=TRUE,sigma=80)
plot(ln)
plot(d)


library(ggplot2)

hist(nndist(ln),breaks=120,xlim=c(0,120))

sum(nndist(ln)<=1)

range(nndist(ln))

```
The minimum distance is 0, which seems questionable. It turns out there are 6 pairs of points centered at the same xy coordinate with different pixel sizes. All 6 pairs of points are marked by the machine learning model(i.e. roi_source=MBP). We need to further clarify whether the points are the same points being identified twice or they are doublets. The duplicated points also indicate that the pixel_size might a biased estimator for the cell size.

```{R}
aaa<-df_full
aaa[3]<-NULL
sum(duplicated(aaa))

CheckUnique<-function(object){
 
  return(!any(duplicated(object)))
}
CheckUnique(df_full)
CheckUnique(aaa)

head(aaa)
View(aaa)
which(duplicated(aaa))

ls<-list(aaa[824,],
         aaa[1159,],
         aaa[1178,],
         aaa[2463,],
         aaa[2796,],
         aaa[3102,])
ls
ls2<-list(df_full[824,],
          df_full[1159,],
          df_full[1178,],
          df_full[2463,],
          df_full[2796,],
          df_full[3102,])
ls2

filter(df_full,com_x==1433,com_y==1484)
```
For the purpose of analysis, we removed the duplicated points for the moment. Then we can find minimal distance between the points and then compute the corresponding scale. The range of of nearest distance is 1, which is 1 pixel in the original image. Checking the graph, it highly possible to be a doublet. We need to come up with a different method. Meanwhile, we may be able to filter out the doublets by theresholding the nearest distance.

```{R}
??distinct
df_full[4]<-NULL
df_sub<-distinct(df_full[c(1,2)])

hist(nndist(df_sub),breaks=100)

range(nndist(df_sub))

which(nndist(df_sub)==1)

View(df_sub)
df_sub[315,]

length(df_sub)

t = seq(0,1500,by=20)
plot(df_sub)
+points(x=1093,y=656,col="red")

```
We generated a scatter plot of the MBP dataset in addition to a mariginal plot.
```{R}
#marginal distribution
library(ggExtra)
a<-ggplot(df_full,
   aes( com_x,  com_y,size=pixel_area))+ geom_point(shape = ".")+xlab("x position in pixel")+ylab("y position in pixel")+geom_jitter(width = 0, height = 0.001, alpha = 0.5)+ theme(aspect.ratio = 1)+theme_bw()

ggMarginal(a,type="histogram",fill = "lightgrey")

```

It seems that there are some variation within different layers. For the whole image, it is look like not possion process. However, the MBP cells in upper part may be a completely random process.

The fig displayed the count of observations of each quadrat. After that we perform a chi-square test. P-value is very small, which indicates that we reject the null hypothesis. The process is not CSR.
```{R}
#Tests based on quadrats:quadratcount
library(spatstat)
qq=quadratcount(ln,nx=3,ny=12)
plot(qq)
quadrat.test(qq)
#The result is heavily depend on the choices of r and c
```


```{R}
#Tests based on distances:
## computationally expensive to calculate the nearest neighborhood
##accuracy of the points location is important
gln = Gest(ln)
plot(gln)

ginhomln=Ginhom(ln)
plot(ginhomln,xlim=c(0,35))
eGinhom = envelope(ln, fun=Ginhom, nsim=200,nrank=1)
plot(eGinhom)

eG<-envelope(ln, fun=Gest, nsim=200,nrank=1)
plot(eG)

plot(eG,xlim=c(0,5))

eK<-envelope(ln, fun=Kest, nsim=200, nrank=1)
plot(eK)
plot(eK,xlim=c(0,5))


```
```{R}
#inhomogeneious L function for MBP datasets
Lln=Linhom(ln)
plot(Lln,lty=1)
plot(Lln,lty=1,xlim = c(0,10))

```

```{R}
#paired correlation function

Kinhom(ln)

plot(Kinhom(ln)) 

pcrln=pcf(Kinhom(ln))

plot(pcrln)

```
```{r}
?Kest

?Gest
?Kest
?envelope
?Linhom

```
