---
title: "Point_process_June9"
author: "Hainan Xu"
date: "09/06/2022"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE,warning=FALSE,message=FALSE,echo =FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Point process

I converted the orginal dataset to the dataset with 4 variables: x position, y position, roi_scource,size of the rectangle.

Here is the size distribution of all the points. It shows a right-skewed distribution.

```{r warning=FALSE,message=FALSE,echo =FALSE,fig.align = 'center'}
library("readr")
library("dplyr")

MBP<-read_csv(file.path("..", "data","H07-0500_79205589_179_1_MBP._analysis_results.csv"))%>%
  transmute(x=com_x,
              y=com_y,
              class=roi_source,
            size=pixel_area)
hist(MBP$size)

```

I plot the points based on thier position and the with marginal distributions of the points. More formatting need to be adjusted.

```{r warning=FALSE,message=FALSE,echo =FALSE,fig.align='center',fig}
library(ggplot2)
ggplot(MBP,
   aes(x = x, y = y,color=class)) + geom_point(shape = ".",pch=20) +facet_grid( . ~ class) + guides(col =FALSE)

library(ggExtra)
a<-ggplot(MBP,
   aes(x = x, y = y,size=size)) + geom_point(shape = ".",aes(size=size)) 
a
ggMarginal(a,type="histogram",fill = "lightblue")
```

\newpage
#### Shape
Then, I converted the data as a marked point process. The mark I use is the size of the rectangle. After that, I extracted the shape of the visual cortex based on the points provided. Here `plot(ln)` can plot the whole marked point process, the size of the circle indicate the size of the original rectangle size.
```{R warning=FALSE,message=FALSE,echo =FALSE,fig.align = 'center', fig.cap="Marked Point Process"}
library("spatstat")
ln = with(MBP,
  ppp(x = x, y = y, marks = size, xrange = range(x), yrange = range(y)))
ln

plot(ln)

library("geometry")
coords = cbind(ln$x, ln$y)
chull = convhulln( coords )

pidx = integer(nrow(chull) + 1)
pidx[1:2] = chull[1, ]
chull[1, ] = NA
for(j in 3:length(pidx)) {
  wh = which(chull == pidx[j-1], arr.ind = TRUE)
  stopifnot(nrow(wh )== 1)
  wh[, "col"] = 3 - wh[, "col"] ## 2->1, 1->2
  pidx[j] = chull[wh]
  chull[wh[, "row"], ] = NA
}
pidx = rev(pidx)

View(pidx)

ggplot(tibble(x = ln$x, y = ln$y)[pidx, ], aes(x = x, y = y)) +
  geom_point() + geom_path() + coord_fixed()

ln = with(MBP,
   ppp(x = x, y = y, marks = class, poly = coords[rev(pidx), ],
       check = FALSE))
ln
```
\newpage
#### Voronoi Tessilation
This is the Voronoi tessilation using `deldir` package.
```{R fig.align = 'center'}
library(deldir)

# Data

x <- MBP$x
y <- MBP$y

# Calculate Voronoi Tesselation and tiles
tesselation <- deldir(x, y)
tiles <- tile.list(tesselation)

plot(tiles,pch=10,showpoints = FALSE)


plot(tiles, pch = 1,
     col.pts = "white",
     border = "white",
     fillcol = hcl.colors(50, "viridis"),
    showpoints = FALSE
     ) 



```


\newpage
#### First order effect: estimation of the intensity.
This is the estimation of the intensity of the MBP cells. 

```{R warning=FALSE,message=FALSE,echo =FALSE,fig.align = 'center'}
d = density(subset(ln, marks == "MBP"), edge=TRUE, diggle=TRUE)
plot(d)
```
\newpage
#### Second order effect: distance to it's nearest neighbor.

Used 3 different edge effect correction. Here, only the correlation of margin is calculated since there are too much point.

G(r) is the cumulative distance, r is the distance. 
```{R warning=FALSE,message=FALSE,echo =FALSE,fig.align = 'center'}
gln = Gest(ln)
gln

library("RColorBrewer")
plot(gln, xlim = c(0, 100), lty = 1, col = brewer.pal(4, "Set1"))

?density

```
Paired correlation function
```{R warning=FALSE,message=FALSE,echo =FALSE,fig.align = 'center'}

Lln = Linhom(subset(ln, marks == "MBP"))
Lln
pcfln = pcf(Kinhom(subset(ln, marks == "MBP")))
plot(pcfln, lty = 1)
plot(pcfln, lty = 1, xlim = c(0, 10))
```

\newpage

## Similar Analyais for a different pic:
```{R,fig.align = 'center'}
MBP2<-read_csv(file.path("..", "data","H07-0500_79205589_179_2_MBP._analysis_results.csv"))%>%
  transmute(x=com_x,
              y=com_y,
              class="MBP")

MBP2

ln2 = with(MBP2,
  ppp(x = x, y = y, marks = class, xrange = range(x), yrange = range(y)))
ln2

ggplot(MBP2,
   aes(x = x, y = y, col = class)) + geom_point(shape = ".") +
   facet_grid( . ~ class) + guides(col =FALSE)

d2 = density(subset(ln2, marks == "MBP"), edge=TRUE, diggle=TRUE)
plot(d2)

gln2 = Gest(ln2)


library("RColorBrewer")
plot(gln2, xlim = c(0, 10), lty = 1, col = brewer.pal(4, "Set1"))

pcfln2 = pcf(Kinhom(subset(ln2, marks == "MBP")))
plot(pcfln2, lty = 1)
plot(pcfln2, lty = 1, xlim = c(0, 10))

```

