---
title: "June_2"
author: "Hainan Xu"
date: "02/06/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# MBP Feature extraction and analysis
Here I used cropped picture(this is all I have) as an example. There are mainly 2 steps:    
1. Threshold the image, then compute the features;    
2. Use the features to compute intensity estimation and other graphs.
## Step1: Feature extraction


Load the package and previewthe image.

```{r read image}
library(BiocManager)
library(EBImage)
im=readImage("/Users/hainanxu/Documents/spatial_visual_cortex/data/im3.jpg")
display(im,method="raster")
hist(im)
```
Check the histogram, we can see that there are 3 colors in the histogram, and they are interlaced. To make the segementation easier, we convert them to greyscale(using the red channel).
```{r pressure, echo=FALSE}
hist(im,xlim=c(0,1))
im = channel(im,"r")
hist(im)
```
Take a look at greyscaled `im`.
```{R}
display(im,method="raster")
#w = makeBrush(size = 30, shape = "gaussian", sigma = 2)
#nucSmooth = filter2(getFrame(r, 1), w)
#display(nucSmooth)
#display(nucSmooth<0.3)
```
After that, we apply a simple method to threshold our greyscale image `im`.
```{R}
hist(im)
display(im<0.25)
rThresh=im<0.25
rOpened = EBImage::opening(rThresh,
                            kern = makeBrush(3, shape = "disc"))
display(rOpened)
rRGB=toRGB(rOpened)
display(rRGB,method="raster")
writeImage(rRGB, "Ahad_June3.tiff", quality = 100)
```
After thresholing our image, we segment it into different objects.
```{R}
rSeed = bwlabel(rOpened)
display(colorLabels(rSeed),method="raster")
```
Here we computed the features of this slice of image. There are 84 features in total, including shape features and moment features of the MBP cell. We create a new dataframe to store the 3 features that we need right now. The 3 features includes: x coordinate, y coordinate, area of each object. After this, we can convert it to a `ppp` object.

```{R}
rSeed=bwlabel(rOpened)
table(rSeed)
F1 = computeFeatures(rSeed,im, xname = "r",
                     refnames = "r")
```
## Step2: Intensity estimation and other graphs
First, create a new dataframe `MBP`. We can explore the distributions of the cells by computing the marginal distribution.
```{R}
library(ggplot2)
library(ggExtra)
x_coord<-F1[,1]
y_coord<-F1[,2]
size<-F1[,6]

range(size)

View(F1)

 MBP<-data.frame(x=x_coord,
              y=y_coord,
              size=size
          )
 
range(size)
 
head(MBP)

a<-ggplot(MBP,
   aes(x = x, y = y,size=size)) + geom_point(shape = ".",aes(size=size)) 
a
ggMarginal(a,type="histogram",fill = "lightblue")
```
Secondly, convert `MBP` as a porint process object. Here each circle indicates a cell, and the size of the cell is corresponding to the area each cell as occupied in pixel.
```{R}
library("spatstat")
ln = with(MBP,
  ppp(x = x, y = y, marks = size, xrange = range(x), yrange = range(y)))
plot(ln)

summary(ln)
plot(Kest(ln))

plot(envelope(ln,Kest)) #envelope

plot(density(ln))


```
Thirdly, we can explore the first order effect: estimate the intensity of this particular region.
```{r}
d = density(subset(ln), edge=TRUE, diggle=TRUE)
plot(d)


```
Fourthly, we can explore the second order effect: randomly pick a point, what is the distance to it's nearest neigbor?

G function: the cumulative distribution function of the distance. Here the purple line indicates the possion process. The second graph is the zoomed in version of the first graph.
```{R}

gln = Gest(ln)
gln
library("RColorBrewer")
plot(gln, xlim = c(0, 50), lty = 1, col = brewer.pal(4, "Set1"))
plot(gln, xlim = c(0, 10), lty = 1, col = brewer.pal(4, "Set1"))
```
Ripley’s K function: for estimation and visualization, transfer K function as L function.
```{R}
Lln = Linhom(ln)
plot(Lln)
```
Paired correlation function:
```{R}
pcfln = pcf(Kinhom(ln))
plot(pcfln, lty = 1)
plot(pcfln, lty = 1, xlim = c(0, 10))

```
Voronoi tessellation:
```{R}
library(deldir)

# Calculate Voronoi Tesselation and tiles
tesselation <- deldir(x_coord, y_coord)
tiles <- tile.list(tesselation)

plot(tiles,pch=10,showpoints = TRUE)

```